Nested sampling with multiple scalars

### 2015-05-29 Paper/ms.tex
References and notation

\newcommand{\xx}{\mathbf{x}}	% The unknown parameters
\newcommand{\dx}{d^N\mathbf{x}} % Volume element in parameter space
\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\parindent=0cm

@@

\section{Introduction}
Nested Sampling \citep{skilling} is an effective and popular
Monte Carlo algorithm for Bayesian computation and statistical mechanics.
In a Bayesian inference problem with unknown parameters denoted collectively
by a vector $\mathbf{x}$, the
posterior distribution for the parameters is
\begin{eqnarray}
p(\mathbf{x} | {\rm data}) &=&
\frac{p(\mathbf{x})p({\rm data} | \mathbf{x})}{p(\rm data)}\\
&=& \frac{\pi(\xx)L(\xx)}{Z}
\end{eqnarray}
where $\pi(\xx)$ is the prior distribution, $L(\xx)$ is the likelihood
function, and $Z$ is the normalising constant, known as the
``marginal likelihood'' or the ``evidence'':
\begin{eqnarray}
Z &=& \int \pi(\xx) L(\xx) \, \dx.
\end{eqnarray}

@@

\section{Demonstration Example}
The prior is a uniform distribution over the $n$-dimensional unit hypercube:
\begin{eqnarray}
p(\mathbf{x}) &=& 1
\end{eqnarray}
as long as $x_i \in [0, 1]$ for all $i$. The scalars are:
\begin{eqnarray}
S_1(\mathbf{x}) &=& -\sum_{i=1}^n \left(x_i - 0.5\right)^2\\
S_2(\mathbf{x}) &=& -\sum_{i=1}^n \sin^2\left(4\pi x_i\right)
\end{eqnarray}

@@

>>>>

\newcommand{\xx}{\mathbf{x}}	% The unknown parameters
\newcommand{\data}{\mathbf{D}}  % The data
\newcommand{\dx}{d^N\mathbf{x}} % Volume element in parameter space
\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\parindent=0cm

@@

\section{Introduction}
Nested Sampling \citep{skilling} is an effective and popular
Monte Carlo algorithm for Bayesian computation and
statistical mechanics
\citep{2009arXiv0906.3544P, 2014PhRvE..89b2302P, 2015arXiv150303404B}.
In a Bayesian inference problem with unknown parameters denoted collectively
by a vector $\xx$, the
posterior distribution for the parameters given data $\data$ (and prior
information $I$) is:
\begin{eqnarray}
p(\xx | \data, I) &=&
\frac{p(\xx | I)p(\data | \xx, I)}{p(\data | I)}\\
&=& \frac{\pi(\xx)L(\xx)}{Z}
\end{eqnarray}
where $\pi(\xx)$ is the prior distribution, $L(\xx)$ is the likelihood
function, and $Z$ is the normalising constant, known as the
``marginal likelihood'' or the ``evidence'':
\begin{eqnarray}
Z &=& \int \pi(\xx) L(\xx) \, \dx.
\end{eqnarray}

@@

\section{Demonstration Example}
The prior is a uniform distribution over the $n$-dimensional unit hypercube:
\begin{eqnarray}
p(\xx) &=& 1
\end{eqnarray}
as long as $x_i \in [0, 1]$ for all $i$. The scalars are:
\begin{eqnarray}
S_1(\xx) &=& -\sum_{i=1}^n \left(x_i - 0.5\right)^2\\
S_2(\xx) &=& -\sum_{i=1}^n \sin^2\left(4\pi x_i\right)
\end{eqnarray}

@@

\bibitem[Baldock et al.(2015)]{2015arXiv150303404B} Baldock, R.~J.~N., 
P{\'a}rtay, L.~v.~B., Bart{\'o}k, A.~P., Payne, M.~C., Cs{\'a}nyi, G.\ 
2015.\ Determining pressure-temperature phase diagrams of materials.\ ArXiv 
e-prints arXiv:1503.03404.

\bibitem[P{\'a}rtay et al.(2014)]{2014PhRvE..89b2302P} P{\'a}rtay, L.~B., 
Bart{\'o}k, A.~P., Cs{\'a}nyi, G.\ 2014.\ Nested sampling for materials: 
The case of hard spheres.\ Physical Review E 89, 022302.

\bibitem[P{\'a}rtay et al.(2009)]{2009arXiv0906.3544P} P{\'a}rtay, L.~B., 
Bart{\'o}k, A.~P., Cs{\'a}nyi, G.\ 2009.\ Efficient sampling of atomic 
configurational spaces.\ ArXiv e-prints arXiv:0906.3544.
